MSDS6372Project1

### 2021-02-02 MSDS6372Project1.Rmd
adding interaction to objective 2 regression

@@

>>>>

######################################################################################################################
# Try Log(MSRP) Second degree EngineHP, adding interaction EngineFuelType*EngineCylinders variable selection #########
######################################################################################################################

tryplot = train%>% select(MSRP,EngineCylinders,EngineFuelType)
tryplot$logMSRP = log(tryplot$MSRP)
tryplot %>% ggplot(aes(x=EngineCylinders,y=logMSRP, color=EngineFuelType))+
  geom_point(position="jitter")+ scale_color_viridis_d()
#Try with LASSO variable selection
x <- model.matrix(log(MSRP)~.+I(EngineHP^2)+EngineFuelType*EngineCylinders,train)[,-1]
y <- log(train$MSRP)
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out3=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out3)
coef(cv.out3, cv.out3$lambda.min)
# - Hatchback - Popularity
# Refit the model with predictors
lasso.lm.log.sq.int = lm(log(MSRP)~.+I(EngineHP^2)-Hatchback-Popularity+EngineFuelType*EngineCylinders,data=train)
summary(lasso.lm.log.sq.int) # R-Squared and Adjusted R-squared is slightly lower compared to regular MSRP using LASSO
# Check Assumptions
par(mfrow=c(2,2))
plot(lasso.lm.log.sq.int)
library(olsrr)
ols_plot_cooksd_bar(lasso.lm.log)
ols_plot_resid_stand(lasso.lm.log)

@@

# LogMSRP with Second Degree EngineHP and interaction EngineCylinders*EngineFuelType
lasso.log.sq.int.pred = predict(lasso.lm.log.sq.int,test)
# Recover the value by exp
lasso.log.sq.int.pred = exp(lasso.log.sq.int.pred)
testASE_LASSO_LOG_Inter = mean((test.result-lasso.log.sq.int.pred)^2)
sqrt(testASE_LASSO_LOG_Inter) #test RMSE = 4990.447
